Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
edit all captions

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$.}
    \label{fig:cube535}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{rockstuhl_rectangles.pdf} 
    \caption{Rockstuhl runs configurations}
    \label{fig:rectangle_sketch}
\end{figure}

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14b.pdf}} 
    \caption{Effect of the elongation of the third direction ($y$) on the 
        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
        and $b=328$ nm, submerged in air and under a constant electric field 
        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
        right plot corresponds to a configuration such that the electric field is 
        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
    \label{fig:ext_y_14}   
 \end{figure}

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
    \caption{ Effect of uniformity and roundness on the mesh on the 
    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the z-axis}
    \label{fig:tri_reg_round_14}
 \end{figure}

@@

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl et al.\ 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}

@@

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
800--1000 $cm^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{ellis_ang_inc.pdf} 
    \caption{Diagram of angles of incidence in \pygbe setup to comply with Ellis et al. disposition.}
    \label{fig:ellis_ang_inc}
 \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{AR_22_vs_norm.pdf} 
    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
             22 degrees incidence.
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

\begin{table}
    \begin{center}
      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
      \label{tab:ar_peaks}
      \begin{tabular}{c c c c c c c c}
        \textbf{AR} \\
        \hline
        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
      \end{tabular}
    \end{center}
  \end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016. Wave
    number at which happens the $E^{\parallel}_{100}$ mode for different aspect ratios.}
    \label{fig:rep_FS4_ellis}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
    \caption{\pygbe vs experiments of figure 2a of Ellis 2016. Ellis data 
    was digitized with web digitizer.}
    \label{fig:pygbe_vs_exp_2a}
 \end{figure}

@@

Since our simulations do not take into account coupling effects, we cannot strictly match 
the conditions to validate our solver. However, from Figure S4 in the supplementary 
materials of Ellis et al., we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^{-1}$. Therefore, as a \textit{first-order correction} we can 
subtract this value from our simulations to account for coupling effects. In Figure 
\ref{fig:val_2a}, we present the result after applying this correction for coupling effects.
It is worth mentioning that the far-left (837 cm$^{-1}$) and far-right (964 cm$^{-1}$) peaks 
on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
what goes beyond theirs \cite{ellis2016} and our paper. They concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
Figure 2 of their paper (green curve), we get Figure \ref{fig:rep_2a}.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$, for two mesh sizes as shown in the legend.}
    \label{fig:cube535}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{rockstuhl_rectangles.pdf} 
    \caption{Configurations for the simulations corresponding to Fig. 14 of Rockstuhl et al., 2005.}
    \label{fig:rectangle_sketch}
\end{figure}

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14b.pdf}} 
    \caption{Effect of the elongation of the third dimension ($y$) on the 
        extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm 
        and $b=328$ nm, submerged in air and under a constant electric field 
        parallel to the $z$-axis. The left plot corresponds to a configuration such that the electric 
        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
        right plot corresponds to a configuration such that the electric field is 
        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}.}
    \label{fig:ext_y_14}   
 \end{figure}

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
    \caption{Effect of uniformity of the mesh and roundness of the edges on the 
    extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the $z$-axis.}
    \label{fig:tri_reg_round_14}
 \end{figure}

@@

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of the results in Figure 14 of Rockstuhl et al., 2005. Extinction cross-section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the $z$-axis.}
    \label{fig:rep_14}
 \end{figure}

@@

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{ellis_ang_inc.pdf} 
    \caption{Diagram showing the angles of incidence in our simulation setups to comply with the configuration in the case from Ellis et al.}
    \label{fig:ellis_ang_inc}
 \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{AR_22_vs_norm.pdf} 
    \caption{Extinction cross-section across wavenumbers for SiC pillars of varying aspect ratios,  
             ($H=950$ nm, $W=400$ nm, $L=400$--$2800$ nm, $AR=1$--$7$), with both normal incidence and a 
             22-degree incidence.
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

\begin{table}
    \begin{center}
      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
      field is parallel to the length ($L$) of the pillar. We have normal incidence and 22-degree incidence.}
      \label{tab:ar_peaks}
      \begin{tabular}{c c c c c c c c}
        \textbf{AR} \\
        \hline
        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
      \end{tabular}
    \end{center}
  \end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 in the supplementary materials of Ellis et al., 2016. Wave
    number at which the $E^{\parallel}_{100}$ mode happens for different aspect ratios.}
    \label{fig:rep_FS4_ellis}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
    \caption{\pygbe vs.\ the experiments presented in Figure 2a of Ellis et al., 2016 (we obtained the data 
    digitizing by hand from their figure using WebPlotDigitizer).}
    \label{fig:pygbe_vs_exp_2a}
 \end{figure}

@@

Since our simulations do not take into account coupling effects in an array of prisms, we cannot strictly match 
the conditions to validate our solver. However, from Figure S4 in the supplementary 
materials of Ellis et al., we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^{-1}$. Therefore, as a \textit{first-order correction} we can 
subtract this amount from our simulations to account for coupling effects. In Figure 
\ref{fig:val_2a}, we present the result after applying this correction for coupling effects.
It is worth mentioning that the far-left (837 cm$^{-1}$) and far-right (964 cm$^{-1}$) peaks 
on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
an effect they say is beyond the scope of their analysis \cite{ellis2016}. They concentrate their analysis on the peaks that occur between 864 and 961 cm$^{-1}$.
If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
Figure 2 of their paper (green curve), we obtain Figure \ref{fig:rep_2a}.
